%-------------------------
% Resume in Latex
% Author : CHAN YH
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[a4paper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage[sfdefault]{roboto}
\usepackage{raleway}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------

\begin{center}
    {\fontfamily{Raleway-TLF}\selectfont \huge \textbf{CHAN YI HENG}} \\ \vspace{1pt}
    % \rmfamily \textbf{\Huge \scshape Chan Yi Heng} \\ \vspace{1pt}
    \small {\faPhoneSquare} +65 8862 0913 $|$
    \href{mailto:x@x.com}{{\faEnvelope} \underline{c@chanyh.com}} $|$ 
    \href {https://chanyh.com}{{\faGlobeAsia} \underline{chanyh.com}} $|$
    \href{https://github.com/cyh-chan}{{\faGithub} \underline{cyh-chan}} $|$
    \href{https://www.linkedin.com/in/chanyiheng/}{{\faLinkedin} \underline{chanyiheng}} $|$
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {National University of Singapore}{Singapore, SG}
      {Master of Science in Statistics}{Aug 2026 -- Expected 2027}
    \resumeSubheading
      {Singapore University of Social Sciences}{Singapore, SG}
      {Bachelor of Science (Honours) in Mathematics}{Jan 2022 -- Dec 2025}
    \resumeSubheading
      {Singapore Polytechnic}{Singapore, SG}
      {Diploma in Banking \& Finance}{Apr 2016 -- Mar 2019}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Teaching Assistant}{Jan 2026 -- Apr 2026}
{Singapore University of Social Sciences}{Singapore, SG}
\resumeItemListStart
    \resumeItem{Led weekly tutorials for approximately 30 undergraduate students in Statistical Analysis, covering probability theory, statistical inference, and linear regression.}
    \resumeItem{Developed a structured revision framework synthesizing core theoretical principles to reinforce formal statistical reasoning.}
    \resumeItem{Emphasized rigorous model formulation and assumption diagnostics, cultivating disciplined quantitative problem-solving practices.}
\resumeItemListEnd

\resumeSubheading
{Research Assistant}{Oct 2025 -- Present}
{Singapore University of Social Sciences, University Research Office}{Singapore, SG}
\resumeItemListStart
    \resumeItem{Collaborated on institutional research initiatives, overseeing data preprocessing, validation, and analytical implementation.}
    \resumeItem{Maintained reproducible data integrity and experimental protocols for large-scale psychological datasets.}
    \resumeItem{Synthesized statistical findings into formal technical documentation for principal investigators and academic review.}
\resumeItemListEnd

\resumeSubheading
{Research Intern}{Nov 2024 -- Aug 2025}
{A*STAR, Advanced Remanufacturing and Technology Centre}{Singapore, SG}
\resumeItemListStart
    \resumeItem{Designed deep learning time-series models for FMCG demand forecasting, improving inventory allocation under uncertainty.}
    \resumeItem{Developed an Explainable AI framework leveraging SHAP to quantify feature attribution and validate model consistency.}
    \resumeItem{Reproduced and extended contemporary architectures to strengthen empirical robustness and comparative benchmarking.}
\resumeItemListEnd

\resumeSubheading
{Finance Operations Analyst}{Sep 2021 -- Dec 2021}
{Indeed}{Singapore, SG}
\resumeItemListStart
    \resumeItem{Executed cross-border financial data migrations with strict compliance to international reporting standards.}
    \resumeItem{Optimized operational workflows and data validation processes within Salesforce environments.}
\resumeItemListEnd

\resumeSubheading
{Finance Specialist}{Aug 2019 -- Dec 2021}
{Singapore Armed Forces}{Singapore, SG}
\resumeItemListStart
    \resumeItem{Managed financial operations and budget allocations under central government regulatory frameworks.}
    \resumeItem{Conducted internal audits and risk assessments, reporting governance findings to senior leadership.}
    \resumeItem{Administered operational budgets during COVID-19 deployments with full compliance and transactional accuracy.}
\resumeItemListEnd

\resumeSubheading
{Wealth Management Intern}{Sep 2018 -- May 2019}
{DBS Bank}{Singapore, SG}
\resumeItemListStart
    \resumeItem{Performed quantitative operational analyses to identify system inefficiencies and recommend structural improvements.}
    \resumeItem{Ensured regulatory compliance through detailed validation of Accredited Investor documentation and data controls.}
\resumeItemListEnd

\resumeSubHeadingListEnd

% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

%-----------Research & PROJECTS-----------
\section{Research}
\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{Advanced Statistical Modeling for High-Dimensional Personality Data} $|$ \emph{Dr. Fan Zengyan}}{Oct 2025 -- Present}
\resumeItemListStart
    \resumeItem{Engineered preprocessing pipelines to structure high-dimensional psychometric data for multivariate statistical and machine learning analysis.}
    \resumeItem{Architected multi-stage frameworks integrating PCA, LASSO regularization, and clustering to identify latent structure and condition-specific interaction effects.}
    \resumeItem{Investigated non-linear dimensionality reduction and hybrid modeling strategies to capture geometric and topological structure within feature space.}
    \resumeItem{Benchmarked regularized linear models and ensemble tree-based methods (XGBoost), evaluating stability, sparsity, and predictive generalization.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Multivariate Time Series Forecasting for Equity Price Prediction} $|$ \emph{Dr. Zhou Tianyi}}{Jan 2025 -- Nov 2025}
\resumeItemListStart
    \resumeItem{Developed a multi-horizon return forecasting framework (1-, 5-, 20-day) across NYSE-listed equities.}
    \resumeItem{Conducted systematic comparisons of ARIMA, LSTM, and Transformer-based architectures (PatchTST, N-HiTS) under univariate and multivariate formulations.}
    \resumeItem{Constructed ensemble-based feature selection pipelines using XGBoost (RFE, permutation importance) to isolate economically meaningful technical signals.}
    \resumeItem{Integrated model interpretability techniques to quantify directional sensitivities and multivariate dependencies.}
    \resumeItem{Implemented walk-forward backtesting to assess temporal robustness and out-of-sample stability.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Data-Driven Framework for Enhancing Supply Chain Resilience} $|$ \emph{Dr. Liu Ning}}{Nov 2024 -- Aug 2025}
\resumeItemListStart
    \resumeItem{Designed end-to-end deep learning optimization architectures for inventory control, benchmarking against Predict-Then-Optimize paradigms.}
    \resumeItem{Implemented dilated temporal CNN and Multi-Quantile RNN models to capture long-range dependencies and probabilistic demand distributions.}
    \resumeItem{Developed stochastic simulation environments to generate synthetic multi-SKU inventory data under variable lead times and demand regimes.}
    \resumeItem{Demonstrated cost reductions relative to classical heuristics (Fixed-Order-Quantity, Order-Up-To) through direct cost-function optimization.}
    \resumeItem{Documented methodology and quantitative evaluation in a formal technical report for research dissemination.}
\resumeItemListEnd

\resumeSubHeadingListEnd
      % {\textbf{Personal Website} $|$ \emph{HTML/CSS, JavaScript}}{May 2024 -- Jun 2024}
      % \resumeItemListStart
      %   \resumeItem{Designed and developed a personal website using HTML, CSS, and JavaScript, showcasing strong front-end development skills}
      %   \resumeItem{Deployed the website to a GitHub repository, demonstrating proficiency in version control and collaborative coding practices}
      %   \resumeItem{Hosted the website under a personal domain using Cloudflare, ensuring reliable and secure access with optimized performance}
      %   \resumeItem{Implemented responsive design principles to ensure the website is user-friendly across various devices and screen sizes}
      %   \resumeItem{Utilized Cloudflare services for enhanced security, performance optimization, and efficient content delivery, improving user experience and site reliability}
      % \resumeItemListEnd
      % \resumeProjectHeading
      %     {\textbf{COVID-19 Safe-Entry Clone System} $|$ \emph{HTML/CSS, JavaScript, SQL}}{Sep 2020}
      %     \resumeItemListStart
      %       \resumeItem{Developed a Safe Entry clone system to log visitor entries at various locations during the COVID-19 pandemic, facilitating effective contact tracing}
      %       \resumeItem{Utilized front-end technologies like HTML, CSS, and JavaScript to create a user-friendly interface for seamless visitor check-in}
      %       \resumeItem{Integrated a MySQL database to store visitor logs securely and ensure quick retrieval for health authorities}
      %       \resumeItem{Designed the system to comply with data privacy regulations, ensuring sensitive information is handled responsibly}
      %       \resumeItem{Enhanced the system with real-time reporting features to assist health authorities in tracking and isolating potential COVID-19 clusters efficiently}
      %     \resumeItemListEnd
      % \resumeProjectHeading
      %     {\textbf{Digitalization by Frank, OCBC} $|$ \emph{Microsoft Suite, Adobe XD}}{Apr 2018 -- Jun 2018}
      %     \resumeItemListStart
      %       \resumeItem{Collaborated with a team of four to propose and prototype innovative digitalization strategies aimed at enhancing OCBC Bank's appeal to younger customers}
      %       \resumeItem{Conducted market research to identify the digital banking needs and preferences of the youth demographic, informing the development of targeted solutions}
      %       \resumeItem{Designed user-friendly mobile app features and an intuitive interface to improve user engagement and streamline banking experiences for young customers}
      %       \resumeItem{Developed interactive prototypes using Adobe XD, demonstrating proposed features and enhancements to OCBC stakeholders}
      %       \resumeItem{Presented project findings and prototypes to OCBC executives, providing actionable insights and recommendations for future digital banking initiatives}
      %       \resumeItem{Received positive feedback from OCBC stakeholders, highlighting the potential impact of the proposed digitalization strategies on customer satisfaction and retention}
      %     \resumeItemListEnd


%
%-----------Competency-----------
\section{Competency}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages \& Scripting}{: Python, R, SQL, LaTeX} \\
     \textbf{Development \& Tools}{: Git, VS Code, Visual Studio, Jupyter} \\
     \textbf{Spoken Languages}{: English (Fluent), Mandarin (Native)}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
